\LaTeX\ Author Guidelines for 3DIMPVT Proceedings

### 2012-06-18 3dimpvt/paper.tex
first draft all text ready

%%%%%%%%% ABSTRACT
\begin{abstract}
  Automated 3D modeling of building interiors is useful in applications
  such as virtual reality and environment mapping. Accurate texture
  mapping of these models is vital towards visualizing the data
  gathered by modeling systems and increases overall usability. The
  localization of cameras in 3D scenes with respect to model surfaces
  often suffers from inaccuracies, resulting in visible discontinuties
  when different images are directly projected onto a plane for
  texturing. Previous approaches at minimizing these discontinuities
  suffer from error accumulation when stitching together multiple
  images and do not robustly handle a wide range of camera locations
  and angles. We propose two approaches for reducing discontinuities
  during texture mapping, tailored towards a backpack-mounted data
  acquisition system.
\end{abstract}

@@

The aim of this paper is to present a solution for texture mapping the
3D models generated by indoor modeling systems, with specific
attention given to a human-operated system with higher localization
errors and greater variance in camera locations. The paper is
organized as follows. Section \ref{sec:backpackSystem} provides an
overview of the backpack modeling system from which data and examples
used throughout this paper are from. Section
\ref{sec:textureMappingOverview} describes the general problem of 3D
texture mapping and reviews existing approaches. Section
\ref{sec:textureMappingMethods} describes challenges posed by the
backpack modeling system and presents our two approaches tailored for
walls and floors/ceilings respectively. Section \ref{sec:results} compares results and
presents conclusions.

\section{Backpack Modeling System}
\label{sec:backpackSystem}
Human-operated data acquisition systems provide unique advantages over vehicular-mounted systems in
terms of agility and portability. Unfortunately, human-operated systems also suffer from a lack of
automation and stability, resulting in higher localization variance
and leading to the problems discussed in Section 4.

\subsection{Data Acquisition Hardware}
The backpack modeling system from which our data was collected
contains five 2D laser range scanners, two cameras, an orientation
sensor, and an IMU. The laser
scanners are 40Hz Hokuyo UTM-30LX 2D laser scanners with a 30-meter
range and a 270$^{\circ}$ field of view. These scanners are mounted
orthogonally to one another. The two cameras are Point Grey
Grasshopper GRAS-50S5C units equipped with fisheye lenses, resulting
in a 180$^{\circ}$ field of view. The IMU, a Honeywell HG9900, is a
strap-down navigation-grade sensor which combines three ring laser
gyros with bias stability of less than 0.003$^{\circ}$/hour and three
precision accelerometers with bias of less than 0.245mm/sec$^{2}$. The
HG9900 provides highly accurate measurements of all 6 DOF at 200Hz, and the orientation sensor (OS), an InterSense InertiaCube3,
provides orientation parameters at a rate of 180Hz.
Wearing this backpack, a human operator then takes great care to walk a path such that every wall in the desired indoor environment is passed and scanned lengthwise at least once.

\subsection{Environment Reconstruction}
Using data gathered by the onboard sensors and multiple localization and
loop-closure algorithms, the backpack is localized over its data
collection period, and a 3D point cloud of the environment is
constructed. Approximate normal vectors for each point in the point
cloud are then calculated by gathering neighboring points within a
small radius and processing them with Principal Component Analysis. These normal vectors allow for the classification and
grouping of adjacent points into structures such as walls, ceilings,
floors, and staircases. A RANSAC algorithm is then employed to fit
polygonal planes to these structured groupings of points, resulting in
a fully planar model. This planar model, consisting of multiple 2D
polygonal planes in 3D space, must then be textured by some subset of the images captured by
the backpack's camera.

\subsection{Plane Generalization}
The planes we aim to texture are output by the surface reconstruction
algorithm briefly explained in Section \ref{sec:backpackSystem}.
These planes have arbitrary orientation and include simple rectangular
walls as well as complicated floor planes defined by over 100
vertices. In order to abstract out the difficulties of dealing with
complex geometry, a minimal bounding box is constructed for each
plane, and used as the target for texture mapping. Since the final
texture created will be a standard rectangular image regardless, we
can simply leave the area between the plane boundary and its bounding
box untextured, and make sure to store the plane's original vertices
for future retrieval.

\subsection{Image Association}
\label{sec:imageAssociation}
In order to speed up the texture mapping process, it is prudent to
reduce the amount of potential images being considered for texture
mapping each plane. The backpack modeling system takes 5
pictures/second from both cameras, resulting in each plane being
present in (and capable of being textured mapped by) thousands of
images, at a wide range of distances and angles. Thus, for the sake
of efficiency, it makes sense to associate each plane with a much
smaller list of images. When creating this subset of images to be associated with each
plane, there are three criteria we keep in mind. First, we want such a
subset of images to be capable of texturing the entirety of a plane,
so as to ensure there are no holes in our final texture. Second, we
want all our images to be taken from a relatively close distance to
the plane, and at as much of a direct, head-on angle as possible. This
ensures that the image projects squarely onto our desired plane, with
minimal inclusion of other planes, and we get a texture with high
resolution. Third, we desire an amount of overlap between the images
chosen. This overlap helps us with preprocessing as well as
postprocessing techniques discussed in Sections x and y.

To meet these three criteria, we divide each plane into [X] triangles
of [Y] size (our planes often have fairly complex geometry, hence the
use of triangulation), using an ear-clipping algorithm followed by
further triangular tesselation. For each triangle, we find all images
that can be projected upon the entirety of the triangle, accounting
for occlusion with other planes as well, using the standard
ray-polygon intersection test shown in figure X. Of these images, we
then select the best one according to the heuristic in equation X,
favoring closer distances and more head-on viewing angles. We also
enforce that no two images are chosen such that they were taken within
0.5 meters of eachother. This results in a greatly-reduced set of
images such that each one is objectively the "best" location-wise for
some number of areas on the plane, addressing the first two
criteria. Furthermore, since cameras are only at good angles to
triangles near their center of projection, images will be chosen such
that there is high overlap between them. With this process completed,
we have reduced the amount of candidate images for each plane from
many thousands to around 50, and are ready to begin the texture
mapping process.

@@

In this section, we will discuss the process of texture mapping a
single plane, as the texturing of each of our planes is completely
independent and can even be completed in parallel.

@@

 As
described in the previous section, we are provided with a set of $M$
candidate images for each plane. Each image has a camera matrix $P_i$ for $i=1..M$, which
translates a 3D point in the world coordinate system to a 2D point in
image $i$'s coordinates. A camera matrix $P_i$ is composed of the
camera's intrinsic parameters, such as focal length and image center,
as well as the extrinsic parameters which specify the rotation and
translation of the camera center's position with respect to the world
coordinates at the time that image $i$ was taken. These extrinsic
parameters are determined by the localization hardware and algorithms
mentioned in Section \ref{sec:backpackSystem}. A point $X$ on the
plane in 3D space can be related to its corresponding pixel $x$ in image $i$
through the following equation:

@@

A plane to be textured is defined by four corner vertices $C_1$ to $C_4$ in
world coordinates and a normal vector indicating the front facing side
of the plane. Our goal is to texture this plane using its associated
images, while eliminating any visual discontinuities or seams that
would suggest that the plane's texture was not composed of a single
continuous image.

@@

Ignoring the fact that the camera matrices $P_{1..M}$ are inaccurate,
one can texture map the plane simply by discretizing the plane into
sections and texturing each section with one image. It makes sense to
texture each section by selecting the best image locally, as was done
in \ref{sec:imageAssociation}.

As Figure \ref{fig:naive} demonstrates, this naive mapping approach
leads to significant misalignment between successive tiles. This
suggests that while the errors in the localization system are quite
low, they are not pixel accurate. For photorealistic texture mapping,
either the camera matrices need to be refined such that the
localization is pixel accurate, resulting in a perfect mapping, or
image stitching techniques need to be applied to provide this
illusion. A commonly-used technique for each approach is examined
next.

@@

\section{Our Approach}
Our approach begins with the naive projection of all our images onto separate copies of our plane, such that no projected data is lost. We then perform a series of preprocessing steps to rotate and shift each image's projection such that its overlapping regions with other projections are as seamless as possible. Following this, we perform a basic intensity-matching algorithm across all images, as images taken from different locations have different levels of overall brightness. From here, we assign textures to our planes using one of two methods, dependent on whether they are wall planes or ceiling/floor planes. The reasoning for this is explained in section \ref{sec:whydifferent}. Lastly, we apply alpha blending to smooth out any remaining seams.

\subsection{Preprocessing}
As a starting point, we naively texture map the plane using the given imprecise camera matrices for each image in the set. This is done by discretizing the plane into an arbitrary density of pixels and projecting each pixel into the image plane using the estimated camera matrix $P_i$. We later intend to shift some of these projected images around on the plane and remove some others. Therefore, each image is stored intact in its own data structure so that it can later be merged with the other images on the plane. We use a Hough transform to rotate the projected images such that vertical lines are pointing directly upwards. This can be effective for indoor modeling, since many indoor scenes contain strong vertical lines from features such as doors, wall panels, or rectangular frames.

\subsection{Localization Refinement}

The camera matrices generated by the localization algorithm are imprecise so the images are misaligned. To fix this, we choose to fix the locations in 2D. First we find corresponding points between all pairs of overlapping images using SIFT matches \cite{lowe1999object}. An illustration of this is given in Figure \ref{fig:matches}. The SIFT matches allow us to determine the correct $x$ and $y$ distances between two images on the plane. We already have an estimate of the $x$ and $y$ distances between the two images which was given by the localization algorithms. Soon we will compare the original estimates to the SIFT-based distances and use this to improve the quality of the image locations.

@@

\[
y^T = 
 \begin{pmatrix}
  d_{1,2}, & d_{1,3}, & d_{2,3}, & \hdots & d_{N-2,N-1}, & d_{N-1,N}, &  x_1
 \end{pmatrix}
\]

@@

\subsection{Ceiling/Floor Texturing vs. Wall Texturing}
\label{sec:whydifferent}
The backpack
modeling system described in Section \ref{sec:backpackHardware} was designed to prioritize for
texturing walls. As mentioned previously, the backpack contains two
fisheye cameras, one aimed directly to the left of the backpack
operator, and one aimed directly to the right. Thus, in order to
texture the ceiling above where the operator walked, images from both
cameras must be combined, with their boundaries meeting overhead. Even more problematic, the floor beneath the
backpack is physically obscured by the operator's body, and thus must
be textured by images taken from behind the operator or from the side. This problem of distant cameras at poor angles
is compounded by the fact that the operator's data acquisition path
attempts to fully scan each wall, but not necessarily the entirety of
a floor or ceiling. This means that large swaths of floors and
ceilings are never walked directly over or under, and thus must be
textured by sidelong images taken from further distances and at
oblique angles. Images taken from closer distances are much preferred, as the effects of imprecise localization and camera matrices become multiplied over greater distances. We also strongly prefer head-on images because when images
are projected onto a planar surface at an extreme angle, the resultant
texture ends up spanning a large portion of the plane, applying
low-resolution textures to areas at greater distances from the camera
location.

In short, these factors mean that wall planes are generally associated with a
multitude of upright, uniform images, from a relatively close distance and originally taken head-on at regular intervals, while floors and
ceilings are associated with images taken from all manner of orientations and
distances. This major difference suggests we employ two strategies,
one tailored for each scenario.

\subsection{Texturing Walls}
Because wall images in general are all good candidates for texturing due to their orientation and location, our goal is less about selecting good images for individual texturing, and more about selecting a set of images that together form a good texture.

@@

Because the images associated with ceilings and floors are often captured by cameras at sidelong angles, we must be conservative when texture mapping such planes. Since localization errors compound over distance, we often have candidate images that project well on areas near the camera itself, but much more poorly at greater distances.

Furthermore, as a result of the projection process and cropping due to occlusion, The geometry of the usable texture projected onto the plane for each image is generally complex and difficult to work with.

These problems suggest that we must segment our images to some extent, as many of our images have desired as well as undesired portions. Such segmentation undoubtedly leads to more discontinuities, but floors and ceilings have lame textures

\subsection{Evaluation of Methods}
methods can be used on eachother

\section{NOTES}

\subsection{Occlusion Masking}
not sure where this section should go. it happens after projections,
discussed in texture mapping overview, but it's definitely more of a
preprocessing step.  Before we proceed with texturing our planes, we
need to ensure that each plane's associated images contain only
content that should be mapped onto the target plane in question. From
the above process, images were chosen such that they had an unoccluded
view of one or more trianglular sections upon a plane. This may not
necessarily hold true however for all areas of the plane, as
demonstrated in figure SOMETHING. If images are not modified to mask
out occluded areas, different images could attempt to cover the same
location on a plane with drastically different textures, inevitably
leading to undesireable discontinuities in our final texture.

Fortunately, by virtue of our indoor environments, the vast majority
of surface geometry is either horizontal or vertical, with high
amounts of right angles. This means that the areas we wish to mask out
of our images due to occlusion are nearly always rectangular
areas. Similar to the triangular tesselation performed for image
association above, we split our image into

With the steps in this section completed, we have generalized the
input of our texture mapping problem into rectangular planes that are
associated with a list of good candidate images, and we are ready to
begin the texture mapping process.

4.1 Texturing Floors and Ceilings

4.2 Texturing Walls Since our candidate images for texturing a wall
are all taken from similar distances and orientations relative to our
wall, their individual "qualities" are all fairly similar. We don't
have to worry as much about filtering out bad images; rather we seek
to select some subset of our images which together form a good
texture.

5 Results and Analysis but also occlusion projection thing. door
projected onto wall is fine, door projected onto floor is bad.

\section{EVERYTHING AFTER HERE IS TEMPLATE STUFF}

\section{Introduction}

Please follow the steps outlined below when submitting your manuscript
to the IEEE Computer Society Press.  This style guide now has several
important modifications (for example, you are no longer warned against
the use of sticky tape to attach your artwork to the paper), so all
authors should read this new version.

% -------------------------------------------------------------------------
\subsection{Language}

All manuscripts must be in English.

\subsection{Dual submission}

By submitting a manuscript to 3DIMPVT, the authors assert that it has
not been previously published in substantially similar
form. Furthermore, no paper which contains significant overlap with
the contributions of this paper either has been or will be submitted
during the 3DIMPVT 2012 review period to {\bf either a journal} or any
conference or any workshop.  {\bf Papers violating this condition will
  be rejected}.

If there are papers that may appear to the reviewers to violate this
condition, then it is your responsibility to: (1)~cite these papers
(preserving anonymity as described in Section 1.6 below), (2)~argue in
the body of your paper why your 3DIMPVT paper is non-trivially
different from these concurrent submissions, and (3)~include
anonymized versions of those papers in the supplemental material.

\subsection{Paper length}
3DIMPVT papers may be between 6 pages and 8 pages.  Overlength papers
will simply not be reviewed.  This includes papers where the margins
and formatting are deemed to have been significantly altered from
those laid down by this style guide.  Note that this \LaTeX\ guide
already sets figure captions and references in a smaller font.  The
reason such papers will not be reviewed is that there is no provision
for supervised revisions of manuscripts.  The reviewing process cannot
determine the suitability of the paper for presentation in eight pages
if it is reviewed in eleven.

% -------------------------------------------------------------------------
\subsection{The ruler}
The \LaTeX\ style defines a printed ruler which should be present in
the version submitted for review.  The ruler is provided in order that
reviewers may comment on particular lines in the paper without
circumlocution.  If you are preparing a document using a non-\LaTeX\
document preparation system, please arrange for an equivalent ruler to
appear on the final output pages.  The presence or absence of the
ruler should not change the appearance of any other content on the
page.  The camera ready copy should not contain a ruler. (\LaTeX\
users may uncomment the \verb'\cvprfinalcopy' command in the document
preamble.)  Reviewers: note that the ruler measurements do not align
well with lines in the paper --- this turns out to be very difficult
to do well when the paper contains many figures and equations, and,
when done, looks ugly.  Just use fractional references (e.g.\ this
line is $097.15$), although in most cases one would expect that the
approximate location will be adequate.

\subsection{Mathematics}

Please number all of your sections and displayed equations.  It is
important for readers to be able to refer to any particular equation.
Just because you didn't refer to it in the text doesn't mean some
future reader might not need to refer to it.  It is cumbersome to have
to use circumlocutions like ``the equation second from the top of page
3 column 1''.  (Note that the ruler will not be present in the final
copy, so is not an alternative to equation numbers).  All authors will
benefit from reading Mermin's description of how to write mathematics:
\url{http://www.cvpr.org/doc/mermin.pdf}.

\subsection{Blind review}

Many authors misunderstand the concept of anonymizing for blind
review.  Blind review does not mean that one must remove citations to
one's own work---in fact it is often impossible to review a paper
unless the previous citations are known and available.

Blind review means that you do not use the words ``my'' or ``our''
when citing previous work.  That is all.  (But see below for
techreports)

Saying ``this builds on the work of Lucy Smith [1]'' does not say that
you are Lucy Smith, it says that you are building on her work.  If you
are Smith and Jones, do not say ``as we show in [7]'', say ``as Smith
and Jones show in [7]'' and at the end of the paper, include reference
7 as you would any other cited work.

An example of a bad paper just asking to be rejected:
\begin{quote}
  \begin{center}
    An analysis of the frobnicatable foo filter.
  \end{center}

  In this paper we present a performance analysis of our previous
  paper [1], and show it to be inferior to all previously known
  methods.  Why the previous paper was accepted without this analysis
  is beyond me.

  [1] Removed for blind review
\end{quote}

An example of an acceptable paper:

\begin{quote}
  \begin{center}
    An analysis of the frobnicatable foo filter.
  \end{center}

>>>>

%%%%%%%%% ABSTRACT
\begin{abstract}
  Automated 3D modeling of building interiors is useful in applications
  such as virtual reality and environment mapping. Accurate texture
  mapping of these models is vital towards visualizing the data
  gathered by modeling systems and increases overall usability. The
  localization of cameras in 3D scenes often suffers from inaccuracies, resulting in visible discontinuties
  when images are directly projected onto a plane for
  texturing. Previous approaches at minimizing these discontinuities
  do not robustly handle a wide range of camera locations and angles, and often suffer from error accumulation when stitching together multiple
  images. We propose two variants on a new approach for reducing discontinuities
  during texture mapping, one tailored for optimal images, and one tailored for sub-optimal images.
\end{abstract}

@@

The aim of this paper is to present a solution for texture mapping the
3D models generated by indoor modeling systems, with specific
attention given to a human-operated system with higher localization
errors and greater variance in camera locations. The paper is
organized as follows. Section \ref{sec:backpackSystem} provides an
overview of the backpack modeling system from which data and examples
used throughout this paper originate. Section
\ref{sec:textureMappingOverview} describes the general problem of 3D
texture mapping and reviews existing approaches. Section
\ref{sec:textureMappingMethods} describes our new approach towards texture mapping, as well as unique challenges posed by the
backpack modeling system and our two approaches tailored for
walls and floors/ceilings respectively. Section \ref{sec:results}
compares results and presents conclusions.

\section{Backpack Modeling System}
\label{sec:backpackSystem}
Human-operated data acquisition systems provide unique advantages over
vehicular-mounted systems in terms of agility and
portability. Unfortunately, human-operated systems also suffer from a
lack of automation and stability, often resulting in much higher data
variance and localization error. As a result, common methods for
texture mapping often produce poor results, as examined in section
XX. Before discussing how to overcome these challenges, we will first
provide an overview of the backpack modeling system from which our
test data was obtained.

\subsection{Data Acquisition Hardware}
\label{sec:backpackHardware}
The backpack modeling system which we worked with contains five 2D
laser range scanners, two cameras, an orientation sensor, and an
IMU. The laser scanners have a 30-meter range and a 270$^{\circ}$
field of view. The two cameras are equipped with fisheye lenses,
resulting in a 180$^{\circ}$ field of view, and are mounted with one
facing left and one facing right. The IMU provides highly accurate
measurements of all 6 DOF at 200Hz, and is used as a ground truth
reference. The orientation sensor provides orientation parameters at a
rate of 180Hz.

With this backpack actively scanning, a human operator then takes
great care to walk a path such that every wall in the desired indoor
environment is passed and scanned lengthwise at least once.

\subsection{Environment Reconstruction}
\label{sec:environmentReconstruction}
Using data gathered by the onboard sensors and multiple localization
and loop-closure algorithms, the backpack is localized over its data
collection period, and a 3D point cloud of the surrounding environment
is constructed based on the laser scanner readings. Approximate normal
vectors for each point in the point cloud are then calculated by
gathering neighboring points within a small radius and processing them
using principal component analysis. These normal vectors allow for the
classification and grouping of adjacent points into structures such as
walls, ceilings, floors, and staircases. A RANSAC algorithm is then
employed to fit polygonal planes to these structured groupings of
points, resulting in a fully planar model. This planar model,
consisting of multiple 2D polygonal planes in 3D space, must then be
textured by all or some subset of the images captured by the
backpack's camera.

\subsection{Image Association}
\label{sec:imageAssociation}
Before discussing texture mapping, we (something goes here based on whether we take credit for stewarts work or not)

In order to speed up our texture mapping process, it is prudent to
reduce the amount of potential images being considered for texture
mapping each plane. The backpack modeling system takes 5
pictures/second from both cameras, resulting in each plane being
present in (and capable of being textured mapped by) thousands of
images, at a wide range of distances and angles. Thus, for the sake of
efficiency, it makes sense to associate each plane with a much smaller
list of images, preferably some set which contains the most desirable images
according to some metric. Thus we keep three criteria in mind while
selecting such a subset. First, we want our final collection of images
to be capable of covering the entirety of a plane, so as to ensure
there are no holes in our final texture. Second, we want all our
images to be taken from a relatively close distance to the plane, and
at as much of a direct, head-on angle as possible. This ensures that
the image projects squarely onto our desired plane, with minimal
inclusion of other planes, and we end with a texture with high
resolution. Third, we desire an amount of overlap between the images
chosen. This overlap provides us with a buffer in case we shift images
as discussed in Section X, and is also required for the blending
process presented in Section Y.

To meet these three criteria, we divide each plane into small triangles just a few centimers across. Triangulation is used due to the fairly complex
geometry of many of our planes, and is accomplished by using a
standard ear-clipping algorithm followed by further triangular
tesselation. For each triangle, we gather all images that can be
projected upon the entirety of the triangle, accounting for occlusion
with other planes as well, using standard ray-polygon intersection
tests. Of these images, we then select the best one
according to the heuristic in equation X, which favors closer distances
and more head-on projection angles. We also enforce that no two images
are chosen such that they were taken within 0.5 meters of eachother,
so as to reduce our overall amount of images. The end result is a
greatly-reduced set of images such that each one is objectively a good choice for texturing some number of areas on the plane. Furthermore, since cameras are only at good
angles to triangles near their center of projection, and poor
candidates for triangles near their edges, images will be chosen such
that there is high overlap between successive images. With the three criteria satisfied, we have reduced the amount of candidate images for
each plane from many thousands to around 50-100.

\subsection{Occlusion Checking}
Before we proceed with texturing our planes, we need to ensure that
each plane's associated images contain only content that should be
mapped onto the target plane in question. From the above process,
images were chosen such that they had an unoccluded view of one or
more trianglular sections upon a plane. This may not necessarily hold
true however for all areas of the plane, as demonstrated in figure
SOMETHING. If images are not modified to mask out occluded areas,
different images could attempt to cover the same location on a plane
with drastically different textures, inevitably leading to
undesireable discontinuities in our final texture.

Fortunately, by virtue of our indoor environments, the vast majority
of surface geometry is either horizontal or vertical, with high
amounts of right angles. This means that the areas we wish to mask out
of our images due to occlusion are nearly always rectangular
areas. Similar to the triangular tesselation performed for image
association above, we split each image into rectangular pieces, and
perform occlusion checks for a sampling of points within each
piece. For rectangles with occluded points, we then subdivide them
into smaller rectangles, and repeat the process, until we reach some
manually-set recursion limit. To actually occlude out rectangles, we
simply remove their texture, as untextured areas will never be chosen
for texture mapping. We are now ready to begin the texture mapping
process.

@@

In this section, we will discuss the process of texture mapping a
single plane, as the texturing of each of our planes is completely
independent and can be completed in parallel.

@@

 As
described in the previous section, we are provided with a set of $M$
images for each plane. Each image has a camera matrix $P_i$ for $i=1..M$, which
translates a 3D point in the world coordinate system to a 2D point in
image $i$'s coordinates. A camera matrix $P_i$ is composed of the
camera's intrinsic parameters, such as focal length and image center,
as well as the extrinsic parameters which specify the rotation and
translation of the camera's position with respect to the world
coordinates at the time that image $i$ was taken. These extrinsic
parameters are determined by the localization hardware and algorithms
mentioned in Section \ref{sec:backpackSystem}. A point $X$ on the
plane in 3D space can be related to its corresponding pixel $x$ in image $i$
through the following equation:

@@

For the sake of simplicity, we treat all planes as rectangles by generating a minimum bounding box for them. Their original vertices can be recovered later as needed, and used to crop any excess texture. A plane to be textured is thus defined by its bounding box with corners $C_i$ in
world coordinates and a normal vector indicating the front facing side
of the plane. Our goal is to texture this plane using its associated
images, while eliminating any visual discontinuities or seams that
would suggest that the plane's texture was not composed of a single
continuous image.

@@

Ignoring the fact that the camera matrices $P_{1..M}$ are inaccurate,
one can texture map the plane by simply applying textures according to
the image association process and scoring function described in
Section X. This naive mapping approach independently selects the best
texture for each trianglular section on the plane, but it also means
that all of our $M$ images are used for the overall texture, thus
increasing the potential amount of poor image boundaries.

As Figure \ref{fig:naive} demonstrates, this approach leads to many
image boundaries with abrupt discontinuities, due to significant
misalignment between images. One approach also tuned for our datasets
attempted to minimize these discontinuities through more intelligent
image selection, making use of spatial and temporal caching
mechanisms.

\subsection{Mapping with Caching}
In order to reduce the severity of discontinuities between adjacent
triangles, one can texture them with the same image, if possible,
eliminating the discontinuity outright, or by two images taken from
similar positions, such that any texture mismatch is ideally less
pronounced. This is accomplished by adding a 2-level cache to the
native mapping approach, and sorting triangles in an order such that
triangle $t_i$ is adjacent to triangle $t_{i+1}$. When a
triangle is assigned a texture, the image it selected is added to the
level 1 cache, and other images that were taken nearby in time and
location, within a predefined threshold, are added to the level 2
cache. Each subsequent triangle to be textured then searches through
the level 1 cache, selecting the best image according to the same
scoring function, and comparing it to some pre-defined threshold. If
the best image's score is below this threshold, the level 2 cache is
then searched, and then finally if necessary, the set of all images is
searched. In this way, the entire plane is textured, with image reuse prioritized, followed by a preference for nearby images.

This approach is the method previously used by the modeling team
associated with our dataset. Therefore, we will use it as our baseline
when comparing other approaches.  The addition of the caching
structure reduces discontinuities overall, as can be seen in the above
image. Nevertheless, the amount of remaining discontinuities suggests
that image selection alone cannot produce seamless textures.  In order
to produce photorealistic texture mapping, either the camera matrices
need to be refined such that the localization is pixel accurate,
resulting in a perfect mapping, or image stitching techniques need to
be applied to provide this illusion. A commonly-used technique for
each approach is examined next.

@@

\section{Our Approach Overview}
Our approach begins 
with the projection of all our images onto
separate copies of our plane, such that no projected data is covered
and lost. Tis is done by discretizing the plane into an arbitrary density of points, and projecting each point into the image plane using the camera matrix $P_i$. We then perform a series of preprocessing steps to rotate
and shift each image's projection such that its overlapping regions
with other projections are as seamless as possible. From here, we assign textures to our planes
using one of two methods, dependent on whether they are wall planes or
ceiling/floor planes. The reasoning for this is explained in section
\ref{sec:whydifferent}. Lastly, we apply two post-processing steps to smooth out
any remaining seams.

\subsection{Hough Transforms}
Our first step is to use Hough transforms to rotate
the projected images such that any strong near-vertical features are made completely vertical. This is effective for indoor modeling, since many indoor
scenes contain strong vertical lines from features such as doors, wall
panels, or rectangular frames.

\subsection{Localization Refinement}
Our next step is to try and fix misalignment between overlapping images.
We do this by fixing
the locations in 2D. First we find corresponding points between all
pairs of overlapping images using SIFT matches
\cite{lowe1999object}. An illustration of this is given in Figure
\ref{fig:matches}. The SIFT matches allow us to determine feature-based $x$ and $y$ distances between two images on the plane, which we can compare against the $x$ and $y$ distances provided by the camera matrices. With these data points, we can reevaluate where each image should be projected.

@@

\[
y^T =
\begin{pmatrix}
  d_{1,2}, &d_{1,3}, &d_{2,3}, &\hdots &d_{N-2,N-1}, &d_{N-1,N}, &x_1
\end{pmatrix}
\]

@@

\subsection{Ceiling/Floor Texturing vs. Wall Texturing}
\label{sec:whydifferent}
The backpack modeling system, as described in Section
\ref{sec:backpackHardware}, was designed to prioritize for texturing
walls. As mentioned previously, the backpack contains two fisheye
cameras, one aimed directly to the left of the backpack operator, and
one aimed directly to the right. Thus, in order to texture the ceiling
above where the operator walked, images from both cameras must be
combined, with their boundaries meeting overhead. Unlike walls, where
one image generally spans the entire height of a wall, two images are
required to span the width of a ceiling. Even more problematic, the
floor beneath the backpack is physically obscured by the operator's
body, and thus must be textured by images taken from behind the
operator or from the side. This problem of distant cameras at poor
angles is compounded by the fact that the operator's data acquisition
path attempts to fully scan each wall, but not necessarily the
entirety of a floor or ceiling. This means that large swaths of floors
and ceilings are never walked directly over or under, and thus must be
textured by sidelong images taken from further distances and at
oblique angles. These effects are shown in the following figure.

In short, these factors mean that wall planes are generally associated
with a multitude of upright, uniform images, from a relatively close
distance and taken head-on at regular intervals, while floors and
ceilings are associated with images taken from all manner of
orientations and distances. This major difference suggests we employ
two strategies, one tailored for each scenario.

\subsection{Texturing Walls}
Because wall images tend to all be fairly good candidates for
texturing due to their orientation and location, our goal is less
about determining the best images, and more about selecting a set of
images that together form the most seamless texture.

\subsubsection{Cost Functions}

In order to objectively decide which set of images accomplishes this,
we need to decide on an overall cost function. As our goal is to reduce
the seams that occur where two images meet, a simple cost function is
the sum of squared pixel differences in overlapping regions between
every pair of images. This encourages image boundaries to occur in
featureless areas, such as bare walls, on in areas where images are
very well aligned.

Another possible cost function is edge energy, i.e. the sum of the
smoothed gradient of the blended seam regions. Minimizing this
encourages image boundaries to be placed in featureless areas even
more than the first cost function. For the results shown throughout
this paper, the first cost function was used, as the regular
occurrence of featureless areas was not guaranteed in our datasets.

\subsubsection{Image Selection}

Now that we have a cost function defined, we need to mechanically
select the set of images for which the overall cost function is
minimized. Since we aim to cover the entirety of our plane, our
problem is to minimally cover a polygon(our plane) using other
polygons of arbitrary geometry (our image projections), with the added
constraint of minimizing our cost function. This is a complex problem,
though it can be generalized to a number of graph coverage problems,
as depicted in figure X. Returning again to the optimality of our
situation when texturing walls however, we can make a quick
simplification for the sake of efficiency. Given that our wall-texture
candidate images were all taken from a head-on angle, and assuming only minor rotations were made earlier, we can reason
that their projections onto the plane are approximately
rectangular. By discarding any excess texture and cropping them
all to be rectangular, our problem becomes the conceptually simpler
problem of filling a polygon with rectangles, such that the sum of all
edge costs between each pair of rectangles is minimal. An additional
benefit of working with rectangular units is that borders between any
two distinct images in our final texture will be either horizontal or
vertical. Since most environmental features inside buildings are horizontal
or vertical, any seams in our texture will intersect them miniimally
and be less noticeable.

By taking one more shortcut we can simplify our problem down even
further. Since care is taken such that our wall images contain the
floor-to-ceiling range of walls, we generally do not have any wall
images such that one should be projected vertically above the
other. In essence, we need only to ensure horizontal coverage of our
planes, as our images provide full vertical coverage. We can thus
construct a Directed Acyclic Graph (DAG) from the images, again with
edge costs defined by our cost function above, and solve a simple
shortest path problem to find an optimal subset of images with regard
to the cost functions.

\begin{figure}
  \centering
  \includegraphics[width=3in]{DynProg.pdf}
  \caption{Image Selection is done by constructing a graph of sorted
    images. Then we solve a shortest path problem where the edge
    weights represent the cost of a seam between two overlapping
    images.}
  \label{fig:DynProg}
\end{figure}

Figure \ref{fig:DynProg} demonstrates the construction of a DAG from
overlapping images of a long hallway. Images are sorted by horizontal
location left to right, and become nodes in a graph. Directed edges
are placed in the graph from left to right between images that
overlap. The weights of these edges are determined by the cost
functions discussed previously. Next, we add two artificial nodes, one
start node representing the left border of the plane, and one end node
representing the right border of the plane. The left artificial node
has directed edges with equal cost to all images that meet the left
border of the plane, and the right artificial node has directed edges
from all images that meet the right border of the plane.

We now solve the standard shortest path problem from the start node to
the end node. This provides a set of images that completely covers the
plane horizontally, while minimizing the cost of the seams between
images.

In rare cases where the vertical dimension of the plane is not entirely
covered by a chosen image, we are left with a hole where no image was
chosen to texture. Rather than reverting to a 2D-coverage problem, we
can elect to simply fill the hole by selecting images in a
greedy fashion, with respect to the same cost function.

At this point, we have mapped every location on our plane to an image
or images that were selected. Before applying these textures, we will
examine how to accomplish the same mapping for ceilings and floors.

@@

Because the images associated with ceilings and floors are often
captured by cameras at sidelong angles, we must be conservative when
we texture map them. Since localization errors compound over distance,
we often have candidate images that project well on areas near the
camera itself, but much more poorly at the greater distances caused by
higher angles. Using entire images to minimize seams is beneficial for
wall texturing, but it becomes detrimental on ceilings and floors,
since the quality of usable texture varies greatly across any one
image. As evident in the following comparison, ceiling and floor
images often have a very low amount of optimal texture relative to the
projection size. This factor suggests that we should segment our images in some way, as many of our images contain both desired as well as undesired portions.

Such segmentation
implies smaller units of texture, which often leads to more images being
chosen and unfortunately, more boundaries between different images as
a result. This goes strongly against our approach for texturing walls,
in which we attempted to minimize the number of images chosen. Nevertheless, boundaries on
floors and ceilings are less problematic, since floors and ceilings
tend to have fewer noticeable features.

As shown in the above figure, we define
a tile length $l1$ as well as an overlap length $l2$, usually about 5
pixels for each. We then discretize our plane into rectangular tiles
$l1$x$l1$ in size. Each tile is then associated with a square
texture of size $(l1+2l2)$x$(l1+2l2)$, such that it shares a large
overlapping region with its neighboring tiles, allowing for blending afterwards. As in wall texturing, rectangles, rather than triangles, are preferred for the high prevalence of horizontal and vertical features, generally light fixtures and floor and ceiling tiles.

For the actual process of image association, we can reuse the caching method shown earlier. This method will balance selection of the best texture for each tile with some amount of image reuse. Coupled with image rotation and shifting, as well as the usage of rectangles instead of triangles, we end with a much more seamless texture, even without any blending applied yet, as seen below.

\subsection{Blending}
Though our preprocessing steps and image selection attempts above
attempted to minimize all mismatches between images, there are often
cases, where due to geometry or projection inaccuracies, we simply
have unavoidable discontinuities. These can however be partially
treated by applying alpha blending over our seams.  Whether the units
we are blending are rectangularly-cropped images for walls, or
rectangular units for ceilings/floors, we can apply the same blending
procedure.

Our alpha blending technique is widely used, and blends pixels
linearly across overlapping regions. For each pixel within an
overlapping region, we simply multiply its intensity (by a factor from 0 to
1), based on its distance from the image's border, with a cap set at some maximum blending distance. In this way, we
interpolate between two overlapping images, providing a gradual
transition between them. Increasing the overlapping and blending distance
results in a smoother transition, but can also result in more
blurriness. The final output is shown in Figure X.
